Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-08-31 analysis/paper/paper.Rmd
Add Barton 2022 reference

Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010].

>>>>

Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [e.g., @government_of_canada_2016; @vannoorden2017; @ARC2018; @EUCommission2022; @GatesFoundation2022], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010] or drawing attention to the lack of code and data that make the published work less useful [@barton2022].
